%
% File naaclhlt2010.tex
%
% Contact: nasmith@cs.cmu.edu

\documentclass[11pt,letterpaper]{article}
\usepackage{naaclhlt2010}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{biblatex}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\addbibresource{paper.bib}

\title{TITLE HERE}

\author{Ben Reis \\
  Johns Hopkins University\\
  3501 Saint Paul St.\\
  Baltimore, MD 21218, USA\\
  {\tt breis3@jhu.edu}
  \And
  Andrew Zhu \\
  Johns Hopkins University \\
  3700 N. Charles St. \\
  Baltimore, MD 21218, USA\\
  {\tt azhu8@jhu.edu}}

\date{}

\begin{document}
\maketitle
\begin{abstract}
General Game Playing (GGP) programs can learn to play any game it is given a description for. In our project, we aim to use these programs to help generate fun and balanced variants of chess. Our system generates a description using Game Description Language (GDL), and based on gameplay between two GGP players,  
\end{abstract}

\section{Introduction}
%Intro here - what's the problem?
% talk about GDL, METAGAME, automated game design
Automated game design is a relatively new topic in artificial intelligence
research. %TODO more here

% Discussion of goals re: interesting+balanced games; (read and) cite AGD
% paper(s).
% Some simple discussion of GGP and general game analysis

We focus on chess because it is a good model of a larger genre of positional
strategy games, which are both interesting to humans and easily amenable to
generic analysis, potentially by computers. Principles developed for creating
and balancing variants of chess can then be generalized and expanded to cover
a much wider field of games.

\section{Encoding Chess-Like Games}

Researchers in automated game design are presently focused on short, simple
videogames with few rules. As far as we know, it has been many years since
someone attempted to construct a system for generating chess-like games, and the
only language we could discover for encoding such games is no longer being
maintained.

On the analysis side of things, an extension of Datalog called the Game
Description Language has become the standard language for formally specifying
games in a manner that can be understood by generic computer players. As there
are a number of existing players and masters that make use of GDL, we decided to
use it as well.

% Discussion of Metagame terminology (possibly break into sidebar?)
As discussed in \cite{agd1}, Pell \cite{metagame} did a great deal of work to
define "chess-like" games formally, in his Metagame workbench for general game
players. While we did not use the specification language he defined, his
terminology and mathematical work was quite useful. The key terms used here are
described below.

\begin{description}
   \item [Direction Vector] A direction vector \(\langle x,y \rangle\) is simply
      a vector over the chessboard. \(x\) represents a difference in file and
      \(y\) represents a difference in rank. A positive vector represents a move
      away from white and to white's right. For example, one of a knight's
      possible moves can be described by \(\langle 1,2 \rangle\), and a white
      pawn's standard move is in the direction \(\langle 0,1 \rangle\).
   \item [Symmetry] Pell defines \textit{forward}, \textit{side}, and
      \textit{rotation} symmetries for his vectors. \textit{Forward} and
      \textit{side} symmetries negate the \(y\) and \(x\) values of the vector,
      respectively, while the \textit{rotation} symmetry swaps them.
   \item [Leap] A leap describes a move where intervening squares on the board
      do not matter; only the destination square has any effect on the move's
      legality, and only the destination can be affected.
   \item [Ride] A ride is a series of leaps in a particular direction, sometimes
      with a maximum number of repetitions. All squares between the start and
      the end of a ride must be empty. A pawn's first-turn move is a ride with
      length \(2\).
   \item [Hop] A hop is a ride where some of the squares must be contain a
      piece, possibly of a specific type.
\end{description}
% End Metagame stuff

\section{Search Algorithms}

\section{Implementation}
% Decided to have players place pieces to simplify game generation.
\subsection{Generating Pieces}
% talk about balance decisions

\subsection{Encoding the Game}
% talk about encoding decisions in GDL
% cite speedchess; alloyGGP
Encoding chess in GDL presents a number of problems due to the complexity of the
game's state, which involves a great deal of information on which pieces have
moved at all (for pawn moves and castling) and which pieces might move to
certain places (for check and related concepts). All of this is in addition to 

\section{Results}

\section{Discussion}


\section{Comparison to Proposal}


\section{Conclusion}

\section{Future Work}
% talk about refinements; ways to test things.

\printbibliography

% \begin{thebibliography}{}
% 
% \bibitem[\protect\citename{Srivastava et al.}2014]{Srivastava:14}
% Nitish Srivastava, Geoffrey Hinton, Alex Krizhevsky, Ilya Sutskever, and Ruslan Salakhutdinov.
% \newblock 2014.
% \newblock Dropout: A Simple Way to Prevent Neural Networks from Overfitting. {\em Journal of Machine Learning Research},15(2014):1929-1958.
% 
% \bibitem[\protect\citename{Nielson}2015]{Nielson:15}
% Michael Nielson.
% \newblock 2015.
% \newblock Neural Networks and Deep Learning. {\em Determination Press}.
% \newblock http://neuralnetworksanddeeplearning.com
% 
% \bibitem[\protect\citename{RGU}]{RGU}
% Robert Gordon University.
% \newblock The Backpropagation Algorithm.
% \newblock https://www4.rgu.ac.uk/files/chapter3\%20-\%20bp.pdf
% 
% \bibitem[\protect\citename{Repo}2013]{Repo:13}
% M. Lichman.
% \newblock UCI Machine Learning Repository.
% \newblock University of California, School of Information and Computer Science.
% \newblock https://archive.ics.uci.edu/ml
% \end{thebibliography}


\end{document}
